Do We Judge Children's Books by Their Covers? 

### 2024-12-04 paper/paper.qmd
Improve the data section, slight modification of language.

### Text Reviews To Rating Ratio
Text Reviews To Rating Ratio (`text_reviews_ratio`) is the ratio between number of text review and number of ratings. It serves as a measurement of reader engagement and the atmosphere of the reader community. Which can have substantial impact on one's impression of a book.  [@fig-textreviewratio] shows the distribution of books with different number of this ratio, showing readers have different level of engagement for different books. Note this variable displays a weak correlation(correlation = 0.2112446) with year of publication, including this variable in the model will minimize the effect of year of publication in the linear regression model. However we have included both variables in consideration for interpretiblity.

@@

ggplot(book_data, aes(x = as.numeric(text_reviews_ratio))) + 
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Text Review/Ratings Ratio",
    y = "Count(Books)"
  ) +
  theme_minimal()
```
### Title
Title (`title`) is the most visible trait on the front cover of a book. The wording of the title will directly shape one's first impression of the book, and directly determines if one have interest in the book.

@@

## Sampling Approach
Keep in mind that this survey aims to be targets to collect more data one a particularly hard-to-reach group: children. While we also aims at identifying the part of rating pattern in children that are due to adults. Quota sampling is quite suitable for this circumstance, which enables us to place more effort on the groups we want to focus on[@chen2018methods].

@@

A sample survey can be found at: [Link](https://docs.google.com/forms/d/e/1FAIpQLSeIMsn9aL4JJsZOZtFYFiE_HoZZbaU_g5v84bLXZpoZKjtNpQ/viewform?usp=sf_link).Thank @stantcheva2023surveys and @chen2018methods's paper in providing valuable guidance in creating survey.

>>>>

### Text Reviews To Rating Ratio
Text Reviews To Rating Ratio (`text_reviews_ratio`) is the ratio between number of text review and number of ratings. It serves as a measurement of reader engagement and the atmosphere of the reader community. Which can have substantial impact on one's impression of a book.  [@fig-textreviewratio] shows the distribution of books with different number of this ratio, showing readers have different level of engagement for different books. Note this variable displays a weak correlation of 0.211 with year of publication, including this variable in the model will minimize the effect of year of publication in the linear regression model. However we have included both variables in consideration for interpretiblity.

@@

ggplot(book_data, aes(x = as.numeric(text_reviews_ratio))) + 
  geom_histogram(binwidth = 0.05, fill = "skyblue", color = "black", alpha = 0.7) +
  labs(
    x = "Text Review/Ratings Ratio",
    y = "Count(Books)"
  ) +
  theme_minimal()
```
### Title
Title (`title`) is the most visible trait on the front cover of a book. The wording of the title will directly shape one's first impression of the book, and directly determines if one have interest in the book. Which have made it very suitable for our propose, as it may be the variable that has the greatest impact on first impression. However, as a text variable, it may not be easy and require complicated model to process title data.

@@

## Sampling Approach
Keep in mind that this survey aims to be targets to collect more data one a particularly hard-to-reach group: children. While we also aims at identifying the part of rating pattern in children that are due to adults. Quota sampling is quite suitable for this circumstance, which enables us to place more effort on the hard-to-reach groups we want to focus on[@chen2018methods].

@@

A sample survey can be found at: [Link](https://docs.google.com/forms/d/e/1FAIpQLSeIMsn9aL4JJsZOZtFYFiE_HoZZbaU_g5v84bLXZpoZKjtNpQ/viewform?usp=sf_link). Thank @stantcheva2023surveys and @chen2018methods's paper in providing valuable guidance in creating survey.
